Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-02 manuscript/climate_sensitivity_draft.Rmd
Updated paper briefly

We analyzed tree-ring data from the twelve species contributing most to woody aboveground net primary productivity, which together comprised 97% of whole-ecosystem between 2008 and 2013 [@helcoski_growing_2019]. Cores were collected in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. In 2010-2011, cores were collected from randomly selected live trees were selected at random from each species in 2010-2011, with at least 30 of those trees having a diameter at breast height (DBH) of at least 10cm [@bourg_initial_2013]. In 2016-2017, cores were collected from all dead trees found in the annual mortality census [@gonzalezakre_patterns_2016]. Cores were sanded, measured, and cross-dated using standard procedures, as detailed in [@helcoski_growing_2019]. The resulting chronologies have been [published](https://github.com/SCBI-ForestGEO/climate_sensitivity_cores) in association with [@helcoski_growing_2019]: (ITRDB). *is this a database?*

@@

>>>>

We analyzed tree-ring data from the twelve species contributing most to woody aboveground net primary productivity (ANPP), which together comprised 97% of study plot ANPP between 2008 and 2013 [@helcoski_growing_2019]. Cores were obtained in 2010-2011 or 2016-2017 from a breast height of 1.3m using a 5mm increment borer. In 2010-2011, cores were collected from randomly selected live trees were selected at random from each species, with at least 30 of those trees having a diameter at breast height (DBH) of at least 10cm [@bourg_initial_2013]. In 2016-2017, cores were collected from all dead trees found in the annual mortality census [@gonzalezakre_patterns_2016]. Cores were sanded, measured, and cross-dated using standard procedures, as detailed in [@helcoski_growing_2019]. The resulting chronologies have been [published](https://github.com/SCBI-ForestGEO/climate_sensitivity_cores) in association with @helcoski_growing_2019: (ITRDB). *is this a database?*

@@

```{r, SI Table 1, eval=TRUE, echo=FALSE, message=FALSE}
heights <- read.csv("tables_figures/height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = "latex", caption = "Species-specific height regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```
